Introduction to LLL\\``Cryptography''

### 2021-05-25 paper.tex
add gram_schmidt plot
Update lattices description and plot

@@

On the figure \ref{fig:lattice1} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$:

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.7\textwidth]{./img/lattice.png}
    \caption{Lattice spanned by $v, w$}
    \label{fig:lattice1}
\end{figure}

\chapter{LLL}

>>>>

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.5\textwidth]{./img/gram_schmidt.png}
    \caption{Gram Schmidt orthogonalization}
    \label{fig:gram_schmidt}
\end{figure}

If we take $v_1=(4, 1), v_2=(2, 3)$ as basis and apply gram schmidt we obtain $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$ as shown in \ref{fig:gram_schmidt}

@@

On the figure \ref{fig:lattice0} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$, and on \ref{fig:lattice1} the same lattice $L$ with
a different basis.

\begin{figure}[!tbp]
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b0.png}
        \caption{Lattice $L$ of $v, w$}
        \label{fig:lattice0}
    \end{minipage}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b1.png}
        \caption{Lattice $L$ of $v', w'$}
        \label{fig:lattice1}
    \end{minipage}
\end{figure}

% matrix([[0, 0, 1], [1, 1, 2], [1, 2, 1]])
\chapter{LLL}
